Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation

### 2020-08-11 main.tex
Grammarly plugin works again, fixed typos in dot points Removed the network image from before - will need to find easier way to show this, far too complex with tikz

Model-based estimation examples include Aristov paper (which requires a linear model, and a hierarchy of sensors), Farokhi paper (which requires the controller compute entirely in encrypted space and send input back to actuator - supporting only cloud as a service type architectures) and Alexandru paper (which implements a distributed control environment but requires a constant gain matrix K)

@@

In addition to applying suitable encryption schemes to signal processing tasks, care must be taken when converting sensor output into an encryptable homomorphic format. As is the case with our proposed localisation method, real number sensor output doesnot trivially encode to integers such that the homomorphic properties provided by an additive encryption scheme over integers keep the underlying real numbers consistent. Methods for handling the encoding of real numbers such that they can be used in homomorphic encryption exist. Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication (extendable to more but each further multiplication limits the real number size and increases the risk of overflow).

@@

Restate the scenario but more formally. Give concrete example - plane and signal towers.

Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability but in context of localisation as well). Note that learning only the sum in aggregation (as is normal in AO) would in this case tell the navigator the average location and measurements of all sensors, which is fine as it does not disclose any exact sensor.

Passive attacks only from sensors to learn navigator position (Otherwise could do some kind of attack that would send fake measurement and note the change in it's own measurements - possible this would give away average of other sensors' measurements but unclear). Justify by saying sensors need to behave for localisation to work in the first place, for example GPS.

Active attacks from navigator to find sensor location allowed, but assume that weights sent to all sensors are the same. In a wireless setting all sensors would recieve all broadcast weights anyway. While special hardware which would support directional broadcasting and recieving could be used to locate sensors individually this is beyond the scope of what is considered in our problem.

Point out that learning the aggregation of sensor outputs, which contains measurement and location information also means that the average location and measurment of the sensors may be leaked, and is accepted as a part of the leakage as it is inferrable from the aggregation scheme and any functioning model-based localisation where measuremments are not known

@@

Fixed sensor subsets of which only whole subsets can be used at once. Maybe a picture of what this might look like in a high level distributed localisation diagram.

@@

% Maybe rename this to Our Scheme or something like that
\section{Private Weighted Aggregation}
Explain it in overview

\subsection{Proof}
Give the reduction proof here for pWSAO and implicit indistinguishability of weights. alternatively sketch it out here and give reduction in appendix.

@@

\section{Private Localisation with Privacy-Preserving Sensors}
Explain it in overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors.

Explain how leakage of the final aggregation sum to the navigator means leakage of the average sensor location and meausurement to the navigator. This is the reason for the accaptance of this leakage, as we pointed out in the problem statement section.

@@

\subsection{Localisation Measurement Modification}
Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in appendix section, but probablynot needed.

@@

@@

Ensure that timestamps are concatenated with position so that no aggregation values are blinded by the same noise.

% Maybe name the scheme? That would be in the heading here
\subsection{Algorithm}
Piece together the whole algorithm here.

@@

\section{Conclusion}
Future work can include hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods. Can also consider ways of sending less information form the navigator to the sensors at each time step.

>>>>

Model-based estimation examples include Aristov paper (which requires a linear model, and a hierarchy of sensors), Farokhi paper (which requires the controller compute entirely in encrypted space and send input back to actuator - supporting only the cloud-as-a-service type architectures) and Alexandru paper (which implements a distributed control environment but requires a constant gain matrix K)

@@

In addition to applying suitable encryption schemes to signal processing tasks, care must be taken when converting sensor output into an encryptable homomorphic format. As is the case with our proposed localisation method, real number sensor output does not trivially encode to integers such that the homomorphic properties provided by an additive encryption scheme over integers keep the underlying real numbers consistent. Methods for handling the encoding of real numbers such that they can be used in homomorphic encryption exist. Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication (extendable to more but each further multiplication limits the real number size and increases the risk of overflow).

@@

Restate the scenario but more formally. Give a concrete example - plane and signal towers.

Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability but in context of localisation as well). Note that learning only the sum in aggregation (as is normal in AO) would, in this case, tell the navigator the average location and measurements of all sensors, which is fine as it does not disclose any exact sensor.

Passive attacks only from sensors to learn navigator position (Otherwise one could do some kind of attack that would send a fake measurement and note the change in its own measurements - possible this would give away the average of other sensors' measurements but unclear). Any largely incorrect inputs from sensors may also be detectable by comparison to alternative navigator onboard sensors (GPS etc.). Justify by saying sensors need to behave for localisation to work in the first place.

Active attacks from navigator to find sensor location allowed, but assume that weights sent to all sensors are the same. In a wireless setting, all sensors would receive all broadcast weights anyway. While special hardware, which may support directional broadcasting or receiving, could be used to locate sensors individually this is beyond the scope of what is considered in our problem.

Point out that learning the aggregation of sensor outputs, which contains measurement and location information also means that the average location and measurement of the sensors may be leaked, and is accepted as a part of the leakage as it is inferrable from the aggregation scheme and any functioning model-based localisation where measurements are not known

@@

Fixed sensor subsets of which only whole subsets can be used at once. Maybe a picture of what this might look like in a high level distributed localisation diagram. Should consider that this sub-grouping would also mean the leakage of the average sensor/measurement of each subset not all sensors at once. This should be considered when choosing sensor subsets and locations.

@@

% Maybe rename this to Our Scheme or something like that
\section{Private Weighted Aggregation}
Explain it in as an overview

\subsection{Proof}
Give the reduction proof here for pWSAO and implicit indistinguishability of weights. Alternatively, sketch it out here and give reduction proof in the appendix.

@@

\section{Private Localisation with Privacy-Preserving Sensors}
Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?

Explain how leakage of the final aggregation sum to the navigator means leakage of the average sensor location and measurement to the navigator. This is the reason for the acceptance of this leakage, as we pointed out in the problem statement section.

@@

\subsection{Localisation Measurement Modification}
Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.

@@

Additionally increased range accuracy may be possible when sensors know the process model of the navigator, allowing them to run their own filter (more accurate than only measurements but not as accurate as the navigator's estimate from multiple sensors) and use their filtered estimated distance as the scaling factor when computing the modified measurement variance.

@@

Ensure that timestamps are concatenated with the position so that no aggregation values are blinded by the same noise.

% Maybe name the scheme? That would be in the heading here
\subsection{Algorithm}
Piece together the whole algorithm here.
Give the algorithm as pseudocode (including encoding and encryption)

@@

Time results can be captured in one graph. Y-axis is time, X-axis is the number of sensors, each line (different colour) will show how the runtime changes as sensors are increased for different Paillier bit-sizes (at least 3: 512, 1024, 2048). Every data point should be the average over some X number of simulations.

Accuracy plots will describe error due to encoding and the average distance of the sensors to the navigator. All plots will use the same ground truth and initial state and covariance estimates (this way average error at each timestep from multiple runs makes sense).

Plot 1 will plot the RMSE of the average of X runs at each encoding size. A fixed layout of 4 mediumly spaced sensor will be used, and a fixed Paillier bit size.

Plot 2 will plot the RMSE as the average distance of sensors changes. Fixed encoding and Paillier bit size. Vary between 4 layouts where 4 sensors are either very close to the centre (and ground truth, and progressively further out)

Plot 3 will accompany plot 3 and display the 4 layouts (arrow for ground truth and points for the sensors).

A well-defined example.

\section{Conclusion}
Possible future work to consider writing here:
Hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods, ways of sending less information form the navigator to the sensors at each time step, active sensor attacker model, different state encryptions received at sensors.
